A Classical Density-Functional Theory for Describing Water Interfaces

### 2011-08-26 paper/project.tex
revamp empirical parameters section
Tested-on: bingley (Linux 2.6.32-5-amd64)

In order to ensure that the empirical parameters are correct, we test
the vapor pressure (see Figure~\ref{fig:equation-of-state}) and
saturated liquid density (see
Figure~\ref{fig:saturated-liquid-density}) against experimental
values.  To find these densities, we use the ``common tangent'' rule,
as illustrated in Figure~\ref{fig:homogeneous}.

>>>>

The majority of the empirical parameters used in our functional are
taken from the paper of Clark \emph{et al} on developing an optimal
SAFT model for water\cite{clark2006developing}.  This SAFT model
contains five empirical parameters: the hard-sphere radius, an energy
and length scale for the dispersion interaction, and an energy and
length scale for the association interaction.  In addition to the five
empirical parameters of Clark \emph{et al}, we add a single additional
parameter defining the length scale over which the density is averaged
when computing the dispersion free energy.  We use this final
parameter to fit the surface tension, with the result shown in
Figure~\ref{fig:surface-tension}.  Because the SAFT model of Clark
\emph{et al} in overestimates the critical temperature---which is a
common feature of models which do not explicitly treat the critical
point---we cannot correctly describe the surface tension at all
temperatures, and chose to fit it for the temperature range at which
water is liquid at one atmosphere of pressure.

\fixme{I'm not sure if this paragraph belongs here.  Somewhere I think
  it's worth discussing any of these homogeneous plots we include, and
  this might be the right place.  We also might want to include one or
  more of them earlier in the text.  A general rule is that any figure
  that is included should be referenced in the text.  If there's
  nowhere in the text that it fits, then it probably doesn't belong in
  the paper....  So I'm not removing the follwoing bits since it's up
  to you, Jess, whether to remove the figures.  We should
  \emph{definitely} remove some of them.}  For reference, we plot the
predicted vapor pressure (see Figure~\ref{fig:equation-of-state}) and
saturated liquid density (see
Figure~\ref{fig:saturated-liquid-density}) against experimental
values.  To find these densities, we use the ``common tangent'' rule,
as illustrated in Figure~\ref{fig:homogeneous}.
